TBD

### 2024-03-20 doc/paper.tex
Prepare for KR

\usepackage{ijcai23}

\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage[switch]{lineno}

\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage[backgroundcolor=lightgray]{todonotes}

% Comment out this line in the camera-ready submission
\linenumbers

\urlstyle{same}

% the following package is optional:
%\usepackage{latexsym}

% See https://www.overleaf.com/learn/latex/theorems_and_proofs
% for a nice explanation of how to define new theorems, but keep
% in mind that the amsthm package is already included in this
% template and that you must *not* alter the styling.
\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem*{remark}{Remark}
\newtheorem{fact}{Fact}

% PDF Info Is REQUIRED.
% Please **do not** include Title and Author information
\pdfinfo{
/TemplateVersion (IJCAI.2023.0)
}

@@

\DeclareMathOperator{\Dom}{Dom}
\DeclareMathOperator{\Doms}{Doms}
\DeclareMathOperator{\Preds}{Preds}
\DeclareMathOperator{\Vars}{Vars}
\DeclareMathOperator*{\argmin}{argmin}
\newcommand{\expr}{\mathtt{expr}}

@@

\title{Towards Practical First-Order Model Counting}

% \author{
% First Author$^1$
% \and
% Second Author$^2$\and
% Third Author$^{2,3}$\And
% Fourth Author$^4$
% \affiliations
% $^1$First Affiliation\\
% $^2$Second Affiliation\\
% $^3$Third Affiliation\\
% $^4$Fourth Affiliation
% \emails
% \{first, second\}@example.com,
% third@other.example.com,
% fourth@example.com
% }

@@

% <= 200 words
\begin{abstract}
\end{abstract}

@@

\paragraph{Proof of correctness.}
\begin{enumerate}
  \item Define what it means for a formula to be \emph{consistent}.
        \begin{itemize}
          \item The formula (including the mapping of constants to their
                domains) does not mention a domain together with its subdomain
                (i.e., all mentioned domains are pairwise disjoint).
                Specifically, we can't have a subdomain together with its parent
                domain or a subdomain together with a constant that belongs to
                its parent domain.
          \item The target of \texttt{Ref} must also be a consistent formula.
          \item The initial formula is consistent by definition.
        \end{itemize}
  \item Aim to show that Crane works correctly on all consistent formulas.
  \item Prove that, whenever some compilation rule makes the formula $\phi$
        inconsistent, greedy compilation rules will make $\phi$ consistent again
        before $\phi$ encounters non-greedy compilation rules that depend on
        $\phi$ being consistent.
        \begin{itemize}
          \item In particular, prove that shattering and unit propagation will
                always eliminate the parent domain of the domains introduced by
                atom counting.
          \item Constraint removal only applies when it can eliminate the parent
                domain entirely.
          \item Prove this for a particular assumption about which compilation
                rules are set to be greedy. For the greedy algorithm, although
                all rules are applied in a greedy manner, we still assume that
                greedy rules will be applied before non-greedy rules.
        \end{itemize}
  \item In particular, independent partial groundings and atom counting are the
        two classical rules that require the formula to be shattered.
  \end{enumerate}

@@

    \draw[->] (formula) -- (alg1);
    \draw[->] (alg1) -- node[above] {$E$} (simplification);
    \draw[->] (simplification) -- node[above] {$E'$} (compilation);
    \draw[->] (compilation) -- (cpp);
    \draw[->] (sizes) -- (cpp);
    \draw[->] (cpp) -- (count);

    \draw[->,dashed] (alg1) -- node[midway,left] {uses} (crane);
    \draw[->,dashed] (alg1) -- node[midway] {uses} (alg2);
    \draw[->,dashed] (alg1) -- node[midway,right] {uses} (alg3);
  \end{tikzpicture}
  \caption{Using \textsc{Crane2} to compute the model count of formula $\phi$.\
    The formula is compiled into a set of equations $E$, which are then
    algebraically simplified and compiled to a C++ program. This program can
    then be run with different command line arguments to compute the model count
    of $\phi$ for various domain sizes.}
\end{figure*}

@@

\paragraph{Contributions.}
\begin{itemize}
  \item \Cref{sec:identifying}
  \item \Cref{sec:simplifying}
  \item Converting the recursive equations into a C++ program, which can then be
        compiled and executed to obtain numerical values (see \cref{sec:cpp}).
  \item Support for infinite precision integers using the GNU Multiple Precision
        Arithmetic Library.
  \item A new set of benchmarks.
  \item The experiments for Crane and ForcLift are (going to be) more
        comprehensive than any other experimental study performed on (W)FOMC
        algorithms.
  \item Some experiments vs FastWFOMC
  \item A proof of correctness
  \item A proof of completeness
\end{itemize}

@@

@@

\bibliographystyle{named}
\bibliography{paper}

>>>>

\usepackage{kr}

% Use the postscript times font!
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\urlstyle{same}

\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{forest}

% See https://www.overleaf.com/learn/latex/theorems_and_proofs
% for a nice explanation of how to define new theorems, but keep
% in mind that the amsthm package is already included in this
% template and that you must *not* alter the styling.
\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem*{remark}{Remark}
\newtheorem{fact}{Fact}
% TODO: fix styling, check if everything in the header is still needed
% TODO: make sure forest arrows match non-forest arrows

\pdfinfo{
/TemplateVersion (KR.2022.0, KR.2023.0, KR.2024.0)
}

\forestset{
sn edges/.style={for tree={edge={-Latex}}}
}

@@

\DeclareMathOperator{\Dom}{Dom}
\DeclareMathOperator{\Doms}{Doms}
\DeclareMathOperator{\Preds}{Preds}
\DeclareMathOperator{\Vars}{Vars}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\GDR}{GDR}

\newcommand{\expr}{\mathtt{expr}}
\newcommand{\FOtwo}{$\mathsf{FO}^{2}$}

@@

\title{TBD}

% \author{%
% First Author$^1$\and
% Second Author$^2$\and
% Third Author$^{2,3}$\and
% Fourth Author$^4$ \\
% \affiliations
% $^1$First Affiliation\\
% $^2$Second Affiliation\\
% $^3$Third Affiliation\\
% $^4$Fourth Affiliation \\
% \emails
% \{first, second\}@example.com,
% third@other.example.com,
% fourth@example.com
% }

@@

\begin{abstract}
\end{abstract}

@@

\paragraph{Proof of correctness (leave for later).}
\begin{enumerate}
  \item Define what it means for a formula to be \emph{consistent}.
        \begin{itemize}
          \item The formula (including the mapping of constants to their
                domains) does not mention a domain together with its subdomain
                (i.e., all mentioned domains are pairwise disjoint).
                Specifically, we can't have a subdomain together with its parent
                domain or a subdomain together with a constant that belongs to
                its parent domain.
          \item The target of \texttt{Ref} must also be a consistent formula.
          \item The initial formula is consistent by definition.
        \end{itemize}
  \item Aim to show that Crane works correctly on all consistent formulas.
  \item Prove that, whenever some compilation rule makes the formula $\phi$
        inconsistent, greedy compilation rules will make $\phi$ consistent again
        before $\phi$ encounters non-greedy compilation rules that depend on
        $\phi$ being consistent.
        \begin{itemize}
          \item In particular, prove that shattering and unit propagation will
                always eliminate the parent domain of the domains introduced by
                atom counting.
          \item Constraint removal only applies when it can eliminate the parent
                domain entirely.
          \item Prove this for a particular assumption about which compilation
                rules are set to be greedy. For the greedy algorithm, although
                all rules are applied in a greedy manner, we still assume that
                greedy rules will be applied before non-greedy rules.
        \end{itemize}
  \item In particular, independent partial groundings and atom counting are the
        two classical rules that require the formula to be shattered.
  \end{enumerate}

@@

    \draw[-Latex] (formula) -- (alg1);
    \draw[-Latex] (alg1) -- node[above] {$E$} (simplification);
    \draw[-Latex] (simplification) -- node[above] {$E'$} (compilation);
    \draw[-Latex] (compilation) -- (cpp);
    \draw[-Latex] (sizes) -- (cpp);
    \draw[-Latex] (cpp) -- (count);

    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (crane);
    \draw[-Latex,dashed] (alg1) -- node[midway] {uses} (alg2);
    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (alg3);
  \end{tikzpicture}
  \caption{Using \textsc{Crane2} to compute the model count of formula $\phi$.\
    The formula is compiled into a set of equations $E$, which are then
    algebraically simplified and compiled to a C++ program. This program can
    then be run with different command line arguments to compute the model count
    of $\phi$ for various domain sizes.}
\end{figure*}

@@

\paragraph{Contributions (outdated).}
\begin{itemize}
  \item \Cref{sec:identifying}
  \item \Cref{sec:simplifying}
  \item Converting the recursive equations into a C++ program, which can then be
        compiled and executed to obtain numerical values (see \cref{sec:cpp}).
  \item Support for infinite precision integers using the GNU Multiple Precision
        Arithmetic Library.
  \item A new set of benchmarks.
  \item The experiments for Crane and ForcLift are (going to be) more
        comprehensive than any other experimental study performed on (W)FOMC
        algorithms.
  \item Some experiments vs FastWFOMC
  \item A proof of correctness
  \item A proof of completeness
\end{itemize}

@@

\section{Theoretical Results}

\begin{theorem}
  The domain recursion by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}
  can simulate the domain recursion by Van den
  Broeck~\shortcite{DBLP:conf/nips/Broeck11}. This proves that Crane can (still)
  handle \FOtwo.
\end{theorem}

\begin{figure}
  \centering
  \begin{forest}
    for tree={sn edges}
    [$\land_{r}$,circle,draw,name=dr
    [$n_{r}$],
    [$n_{x}$]
    ]
    \draw[-Latex] (dr) to [loop right] node {$\Delta \gets \Delta \setminus \{\,x\,\}$} ();
  \end{forest}
  \begin{forest}
    for tree={sn edges}
    [$\GDR(x \in \Delta)$,ellipse,draw,
    [$\land$,circle,draw,
    [$\bigwedge_{y \in \Delta}$,ellipse,draw]
    [$\land$,circle,draw]
    ]
    ]
  \end{forest}
\end{figure}

\begin{proof}
  `A theory allows for domain recursion when the theory is shattered, the theory
  contains no independent subtheories, and there exists a root binding class.'

  Stuck on some weird cases. Need to prove that the model count of $n_{x}$ will
  never depend on $|\Delta|$.
\end{proof}

@@

\bibliographystyle{kr}
\bibliography{paper}
